Verifying Demonstrations

### 2020-03-13 paper/distance-bounding.tex
Uses acro for DFKO model

There are two lines of attempts at formalizing the above properties: one by 
\citet{DB-BMV} and another by \citet{DB-DFKO}.
We will use the framework of \citeauthor{DB-DFKO} with extensions by 
\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
\cref{DB-definitions}).

@@

The DFKO framework~\cite{DB-DFKO} uses an abstract clock~\(\marker\colon \NN\to 
  \NN\) which is strictly increasing and orders the adversary's actions.
We let
\(\Xscript{\sid}{i, \dotsc, j}\)
denote the sequence of messages
\((m_i, \dotsc, m_j)\)
exchanged during the session \(\sid\).

>>>>

There are two lines of attempts at formalizing the above properties: one by 
\citet{DB-BMV} and another by \citet{DB-DFKO}.
We will use the model of \citeauthor{DB-DFKO} (the \acs*{DFKOmodel}) with 
extensions by \textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions 
in \cref{DB-definitions}).

@@

The \ac{DFKOmodel} uses an abstract clock~\(\marker\colon \NN\to \NN\) which is 
strictly increasing and orders the adversary's actions.
We let
\(\Xscript{\sid}{i, \dotsc, j}\)
denote the sequence of messages
\((m_i, \dotsc, m_j)\)
exchanged during the session \(\sid\).
